Short Paper

### 2024-10-18 02_paper/02_study/01_fitbit_paper/R_scripts/analysis_190423 Kopie.Rmd
x paper

plot_overall
```

@@

table_data <- 
  df_regression %>% 
#  mutate(time = time * 60) %>% 
  split(.$Phase) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      ) %>%
  map(~ tibble(time_span = names(.),
               intercept = fixef(.)[[1]],
               intercept_sd = VarCorr(.) %>% as_tibble() %>% .[1,5],
               intercept_p = coef(summary(.))[1, 5],
               slope = fixef(.)[[2]],
               slope_sd = VarCorr(.) %>% as_tibble() %>% .[2,5],
               slope_p = coef(summary(.))[2, 5]
               )
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = round(intercept, digits = 3),
            `SD(Intercept)` = round(intercept_sd$sdcor, digits = 3),
            `p-Value (Intercept)` = round(intercept_p, digits = 3),
            `Mean(Slope)` = round(slope, digits = 3),
            `SD(Slope)` = round(slope_sd$sdcor, digits = 3),
            `p-Value (Slope)` = round(slope_p, digits = 3)
            )

@@

table_data %>% 
  arrange(Phase) %>% 
knitr::kable(., caption = "Overview")
```

>>>>

lm_plot_phases

ggsave(filename = "plots/test.pdf")
```

@@

table_data <- 
  df_regression %>% 
 # mutate(time = time * 60) %>% 
  split(.$Phase) %>% 
  map(~ lmerTest::lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      ) %>%
  map(~ tibble(time_span = names(.),
               intercept = fixef(.)[1],
               intercept_sd = VarCorr(.) %>% as_tibble(.) %>% .[1,5],
               intercept_p = coef(summary(.))[1, 5],
               slope = fixef(.)[2],
               slope_sd = VarCorr(.) %>% as_tibble(.) %>% .[2,5],
               slope_p = coef(summary(.))[2, 5]
               )
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = intercept,
            `SD(Intercept)` = intercept_sd$sdcor,
            `p-Value (Intercept)` = intercept_p,
            `Mean(Slope)` = slope, 
            `SD(Slope)` = slope_sd$sdcor,
            `p-Value (Slope)` = slope_p, 
            )

@@

table_data %>% 
  arrange(Phase) %>% 
knitr::kable(., caption = "Overview")

model_hurensohn <- 
  df_regression %>% 
  filter(time_span == "teaching") %$% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .) %>% 
  fixef(.)[2]

fixef(model_hurensohn)[2]

model_pre <- 
  df_regression %>% 
  filter(Phase == "Pre Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .)
model_teach <- 
  df_regression %>% 
  filter(Phase == "Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_post <- 
  df_regression %>% 
  filter(Phase == "Post Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_int <- 
  df_regression %>% 
  filter(Phase == "Interview Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_end <- 
  df_regression %>% 
  filter(Phase == "End Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))

tib_pre <-

```{r}
df_regression <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID", "time_span","time","heart_rate_std") %>% 
  distinct() %>% 
  mutate(time = time / 100) %>% 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

fix_models <-
  df_regression %>% 
  split(.$Phase) %>% 
  map(~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
       data = .
       )
      ) %>% 
    map(~ coef(.) %>%
          tibble::as_tibble(.,
                            rownames = "name") %>%
          transmute(type = if_else(str_detect(name,
                                              ":"),
                                   true = "slope",
                                   false = "intercept"),
                    id = str_remove_all(name,
                                        "[^[:digit:]]"),
                    value = value
                    ),

    ) %>% 
    bind_rows(.id = "Phase") %>% 
    pivot_wider(names_from = type,
                values_from = value
                )
p.values_slope <- 
  fix_models %>% 
  split(.$Phase) %>% 
  map(~ t.test(x = .$slope,
             mu = 0)$p.value
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  pivot_longer(cols = everything(),
               names_to = "Phase",
               values_to = "p.value_slope")

p.values_intercept <- 
  fix_models %>% 
  split(.$Phase) %>% 
  map(~ t.test(x = .$intercept,
             mu = 0)$p.value
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  pivot_longer(cols = everything(),
               names_to = "Phase",
               values_to = "p.value_intercept")

sd_mean <- 
  fix_models %>% 
  group_by(Phase) %>% 
  summarize(mean_slope = mean(slope),
            sd_slope = sd(slope),
            mean_intercept = mean(intercept),
            sd_intercept = sd(intercept))

model_teach_fix <- 
  df_regression %>% 
  filter(Phase == "Pre Teaching Phase") %>% 
  mutate(time = time / 60) %>% 
  lm(formula = heart_rate_std ~ 0 + ID + time:ID,
       data = .)

table_data <- 
  right_join(x = sd_mean,
             y = p.values_intercept,
             by = "Phase") %>% 
  right_join(x = .,
             y = p.values_slope,
             by = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = mean_intercept,
            `SD(Intercept)` = sd_intercept,
            `p-Value (Intercept)` = p.value_intercept,
            `Mean(Slope)` = mean_slope, 
            `SD(Slope)` = sd_slope,
            `p-Value (Slope)` = p.value_slope, 
            ) %>% 
  arrange(Phase)

model_teach_fix %>% 
  coef(.) %>% 
  tibble::as_tibble(.,
                    rownames = "name"
                    ) %>% 
  mutate(type = if_else(str_detect(name,
                                   ":"),
                        true = "slope",
                        false = "intercept"
                        )
         ) %>% 
  filter(type == "slope") %$% 
  t.test(x = value,
         mu = 0) -> test

test$

model_pre <- 
  df_regression %>% 
  filter(Phase == "Pre Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .)
model_teach <- 
  df_regression %>% 
  filter(Phase == "Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_post <- 
  df_regression %>% 
  filter(Phase == "Post Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_int <- 
  df_regression %>% 
  filter(Phase == "Interview Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_end <- 
  df_regression %>% 
  filter(Phase == "End Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))

summary(model_teach_fix)

### 2024-10-18 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission.Rmd
x paper

[^5]: Although this procedure does not account for nonmonotonic progressions in individual HR, a graphical evaluation revealed that the linear estimates corresponded well to the majority of the cases (see XX in the supplementary material).

>>>>

[^5]: Although this procedure does not account for nonmonotonic progressions in individual HR, a graphical evaluation revealed that the linear estimates corresponded well to the majority of the cases (see Figures \ref{fig.a3} to \ref{fig.a7} in the supplementary material).

### 2024-10-18 02_paper/02_study/01_fitbit_paper/Submission/analysis_270423.Rmd
x paper

summary(regr_preparation1)
summary(regr_end2)
summary(regr_end3)
summary(regr_post4)

@@

fit_pre_1 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %$% 
  lm(slope ~ teaching_experience)

>>>>

summary(regr_preparation1)
summary(regr_preparation2)
summary(regr_preparation3)
summary(regr_preparation4)
summary(regr_teaching1)
summary(regr_teaching2)
summary(regr_teaching3)
summary(regr_teaching4)
summary(regr_post1)
summary(regr_post2)
summary(regr_post3)
summary(regr_post4)
summary(regr_interview1)
summary(regr_interview2)
summary(regr_interview3)
summary(regr_interview4)
summary(regr_end1)
summary(regr_end2)
summary(regr_end3)
summary(regr_end4)

@@

fit_pre_1 <-
  df_multi %>% 
  filter(Phase == "Pre Teaching Phase") %>% 
  lm(slope ~ teaching_experience,
     data = .)

### 2024-10-18 02_paper/02_study/01_fitbit_paper/Submission/tab_1.tex
x paper

\caption{Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)}

>>>>

\caption{\label{tab:table_1}Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)}

### 2024-10-18 02_paper/02_study/01_fitbit_paper/Untitled/Untitled.tex
x paper

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
  \linenumbers % turns line numbering on
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}

@@

@@

  \title{New approaches to teachers' experience of stress: Do heart rate
measurements with fitness trackers provide an efficient, inexpensive,
and robust measurement method?}
    \author[1]{Mandy Klatt%
  %
  }
   \ead{mandy.klatt@uni-leipzig.de} 
    \author[1]{Peer Keßler%
  %
  }

    \author[1,2]{Gregor Kachel%
  %
  }

    \author[1]{Christin Lotz%
  %
  }

    \author[1]{Anne Deiglmayr%
  %
  }

      \cortext[cor1]{Corresponding author}

  \begin{abstract}
  One or two sentences providing a \textbf{basic introduction} to the
  field, comprehensible to a scientist in any discipline.

  Two to three sentences of \textbf{more detailed background},
  comprehensible to scientists in related disciplines.

  One sentence clearly stating the \textbf{general problem} being
  addressed by this particular study.

  One sentence summarizing the main result (with the words
  ``\textbf{here we show}'' or their equivalent).

  Two or three sentences explaining what the \textbf{main result}
  reveals in direct comparison to what was thought to be the case
  previously, or how the main result adds to previous knowledge.

  One or two sentences to put the results into a more \textbf{general
  context}.

  Two or three sentences to provide a \textbf{broader perspective},
  readily comprehensible to a scientist in any discipline.

  XXX In this proof-of-concept study, we aimed to advance the field of
  teacher stress by collecting heart rate data with wrist-worn devices
  and testing a methodology that has the potential to provide more
  insights on the non-invasive assessment of teacher stress. XXX
  \end{abstract}
    \begin{keyword}
    heart rate; photoplethysmography; wearable electronic device;
teaching \sep 
    heart rate; photoplethysmography; wearable electronic device;
teaching
  \end{keyword}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Seed for random number generation}
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{42}\NormalTok{)}
\NormalTok{knitr}\SpecialCharTok{::}\NormalTok{opts\_chunk}\SpecialCharTok{$}\FunctionTok{set}\NormalTok{(}\AttributeTok{cache.extra =}\NormalTok{ knitr}\SpecialCharTok{::}\NormalTok{rand\_seed)}
\end{Highlighting}
\end{Shaded}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Physiological data such as heart rate are becoming increasingly
important in research on stress experience. They represent an important
indicator of physical or emotional stress, as increased workload is
associated with increased heart rate \citep{sachs2014physiologische}.
Furthermore, they allow a more objective recording of stress than
self-reports \citep{rungeusing}. However, capturing heart rate in an
educational context requires the use of low-cost and non-invasive
instruments. Fitness trackers worn on the wrist have the potential to be
such a useful tool \citep{ferguson2015validity}.

To date, there is still little evidence on the usefulness of heart rate
measurements using fitness trackers in teaching and learning settings
\citep{ertzberger2016use, lowe2016educational}. \citet{rungeusing} alone
examined teacher stress in a relatively small sample (\emph{N} = 4
teachers) and showed that high heart rate indicates more stress in
teachers.

Thus, there remains a lack of robust studies on whether fitness trackers
are an efficient, low-cost, and robust measurement method for assessing
teachers' experience of arousal during teaching.

\hypertarget{theoretical-background}{%
\section{Theoretical Background}\label{theoretical-background}}

\hypertarget{stress-in-teaching-profession}{%
\subsection{Stress in Teaching
Profession}\label{stress-in-teaching-profession}}

--\textgreater{} teacher profession is one of the most stressful
professions.

Teacher stress can be defined as ``{[}\ldots{]} the experience by a
teacher of unpleasant, negative emotions, such as anger, anxiety,
tension, frustration or depression, resulting from some aspect of their
work as a teacher.'' \citep{kyriacou2001teacher}.

Teachers' individual perceptions of student misbehavior in the classroom
are closely related to their well-being \citep{ALDRUP2018126}.

--\textgreater{} wie entsteht Stress

--\textgreater{} wie wurde Stress bisher gemessen

\hypertarget{heart-rate-as-an-indicator-for-stress-or-arousal}{%
\subsection{Heart rate as an indicator for stress or
arousal}\label{heart-rate-as-an-indicator-for-stress-or-arousal}}

Heart rate is physiologically regulated by the autonomic nervous system.
An increase in the activity of the sympathetic as part of the autonomic
nervous system results in the heart rate being speeded up (``fight or
flight''). On the other hand, an increased activity of the
parasympathetic as the counterpart has the effect of slowing down the
heart rate (``rest and digest'') \citep{Battipaglia2015}. In addition to
the autonomic nervous system and genetic factors, heart rate is
influenced by numerous external factors such as social, personal,
psychological, environmental and behavioural factors
\citep{wang2022using}.

\hypertarget{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}{%
\subsection{Wrist-worn devices as a new approach to assess physiological
measures}\label{wrist-worn-devices-as-a-new-approach-to-assess-physiological-measures}}

\citet{fuller2020reliability} showed in their review article that
wearable devices such as Fitbit watches are accurate and reliable for
measuring heart rate in controlled settings.

``The use of physiological measures enabled us to get some insight into
teachers' affective responses without disrupting the teaching process
(Mauss \& Robinson, 2009) and to reduce issues with social desirability,
retrospective bias, and high cognitive load (Becker et al., 2015; Goetz
et al., 2015; Scollon et al.,2009; Wilhelm \& Grossman, 2010). Moreover,
we found that heart rate measures discriminated between both teachers,
even when their interpersonal behavior during the lesson start was
relatively similar.''

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{19}
\tightlist
\item
  (PDF) A Quantitative Exploration of Two Teachers with Contrasting
  Emotions: Intra-Individual Process Analyses of Physiology and
  Interpersonal Behavior. Available from:
  https://www.researchgate.net/publication/329787434\_A\_Quantitative\_Exploration\_of\_Two\_Teachers\_with\_Contrasting\_Emotions\_Intra-Individual\_Process\_Analyses\_of\_Physiology\_and\_Interpersonal\_Behavior
  {[}accessed Dec 07 2022{]}.
\end{enumerate}

\hypertarget{aim-of-the-study}{%
\subsection{Aim of the study}\label{aim-of-the-study}}

In the present study, we assessed HR measures and self-report data of
pre- and in-service teachers in a controlled teaching-learning setting.
The aim was to investigate whether heart rate measurements using
wrist-worn fitness trackers are a suitable and effective method
\textbf{(1)} to map differences in states of arousal between five
different phases (pre-teaching phase, teaching phase, post-teaching
phase, interview phase and end phase) and \textbf{(2)} to evaluate the
correlation between self-reported evaluations and HR measures.

\textbf{(H1)} We expected heart rates to be higher during the teaching
phase than during the pre- and the three post-teaching phases, and that
the HR measures would decrease over the course of the study.
\textbf{(H2)} We also predicted that HR and a high ranking on the
negative scale on our survey (feeling disturbed by disruptions) would
correlate positively and a high ranking on the positive scale (feeling
confident in dealing with disruptions) would follow the inverse pattern.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if
any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\bibliography{r-references.bib}

>>>>

  \journal{An awesome journal} % Sets Journal name

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Short Paper},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}

\setcounter{secnumdepth}{5}
% Pandoc toggle for numbering sections (defaults to be off)

@@

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

@@

  \title{Short Paper}
    \author[Some Institute of Technology]{Alice Anonymous%
  \corref{cor1}%
  \fnref{1}}
   \ead{alice@example.com} 
    \author[Another University]{Bob Security%
  %
  }
   \ead{bob@example.com} 
    \author[Another University]{Cat Memes%
  %
  \fnref{2}}
   \ead{cat@example.com} 
    \author[Some Institute of Technology]{Derek Zoolander%
  %
  \fnref{2}}
   \ead{derek@example.com} 
      \affiliation[Some Institute of Technology]{
    organization={Big Wig University},addressline={1 main
street},city={Gotham},postcode={123456},state={State},country={United
States},}
    \affiliation[Another University]{
    organization={Department},addressline={A street
29},city={Manchester,},postcode={2054 NX},country={The Netherlands},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

  \begin{abstract}
  This is the abstract.

  It consists of two paragraphs.
  \end{abstract}
    \begin{keyword}
    keyword1 \sep 
    keyword2
  \end{keyword}

@@

Please make sure that your manuscript follows the guidelines in the
Guide for Authors of the relevant journal. It is not necessary to
typeset your manuscript in exactly the same way as an article, unless
you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see
\url{https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions}

\hypertarget{bibliography-styles}{%
\section{Bibliography styles}\label{bibliography-styles}}

Here are two sample references: \citeauthor{Feynman1963118}
\citetext{\citeyear{Feynman1963118}; \citealp{Dirac1953888}}.

By default, natbib will be used with the \texttt{authoryear} style, set
in \texttt{classoption} variable in YAML. You can sets extra options
with \texttt{natbiboptions} variable in YAML header. Example

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{natbiboptions}\KeywordTok{:}\AttributeTok{ longnamesfirst,angle,semicolon}
\end{Highlighting}
\end{Shaded}

There are various more specific bibliography styles available at
\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
To use one of these, add it in the header using, for example,
\texttt{biblio-style:\ model1-num-names}.

\hypertarget{using-csl}{%
\subsection{Using CSL}\label{using-csl}}

If \texttt{citation\_package} is set to \texttt{default} in
\texttt{elsevier\_article()}, then pandoc is used for citations instead
of \texttt{natbib}. In this case, the \texttt{csl} option is used to
format the references. Alternative \texttt{csl} files are available from
\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
and stored locally, or the url can be used as in the example header.

\hypertarget{equations}{%
\section{Equations}\label{equations}}

Here is an equation: \[ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
\]

Here is another: \begin{align}
  a^2+b^2=c^2.
\end{align}

Inline equations: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)

\hypertarget{figures-and-tables}{%
\section{Figures and tables}\label{figures-and-tables}}

Figure \ref{fig2} is generated using an R chunk.

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth]{Untitled_files/figure-latex/fig2-1}

}

\caption{\label{fig2}A meaningless scatterplot.}\label{fig:fig2}
\end{figure}

\hypertarget{tables-coming-from-r}{%
\section{Tables coming from R}\label{tables-coming-from-r}}

Tables can also be generated using R chunks, as shown in Table
\ref{tab1} for example.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{], }
    \AttributeTok{caption =} \StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{label\{tab1\}Caption centered above table"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\label{tab1}Caption centered above table}\tabularnewline
\toprule()
& mpg & cyl & disp & hp \\
\midrule()
\endfirsthead
\toprule()
& mpg & cyl & disp & hp \\
\midrule()
\endhead
Mazda RX4 & 21.0 & 6 & 160 & 110 \\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
Datsun 710 & 22.8 & 4 & 108 & 93 \\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
Valiant & 18.1 & 6 & 225 & 105 \\
\bottomrule()
\end{longtable}

\renewcommand\refname{References}
\bibliography{mybibfile.bib}
